\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-05-14 SQP_Retract_rev1.tex
Very minor edit after the update of numerics

From Table~\ref{table2}, one can see that the recovery errors of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ are comparable, and FPA$_{\rm retract}$ is usually faster, except for the case when $i = 10$.
Indeed, we observe that the performance of FPA$_{\rm retract}$ can be quite sensitive to the ``quality" of the initial point (reflected partly by the RecErr of the approximate solution returned by SPGL1).

>>>>

From Table~\ref{table2}, one can see that the recovery errors of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ are comparable, and FPA$_{\rm retract}$ is usually faster, except for the case when {\color{blue}$i = 6$}.
Indeed, we observe that the performance of FPA$_{\rm retract}$ can be quite sensitive to the ``quality" of the initial point (reflected partly by the RecErr of the approximate solution returned by SPGL1).
